Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-21 journal/article.tex
References from primary docs

@@

>>>>

What is agile?
[6] Conboy K., Fitzgerald B., “Toward a conceptual framework for agile methods:
a study of agility in different disciplines,”
Proc. ACM workshop on Interdisciplinary software engineering research (WISER), 2004, pp. 37-44.

\subsection{Large scale general references from primary studies}

Laanti 2008:
[2] Kähkönen Tuomo, “Agile Methods for large organizations – building communities of practice”.
Proc. Agile Development Conf. (ADC), 2004, pp. 2-10.

[7] Eckstein Jutta, “Agile Software Development in the large: Diving into the deep”,
Dorset House Publishing, 2004. ISBN 0-932633-57-9.
[8] Leffingwell Dean, “Scaling Software Agility: Best Practices for Large Enterprises”,
Addison-Wesley Professional, 2007. ISBN-10: 0321458192.
[12] Highsmith J., Agile for the Enterprise, “From Agile Teams to Agile Organizations”,
Cutter, 2005. http://www.cutter.com/program/ fulltext/reports/2005/01/index.html .
[13] Schwaber Ken, “Enterprise and Scrum”, Microsoft Press 2007, ISBN-10: 0735623376.

@@

----

Moore and Spens \cite{Moore2008} define large scale global development in the
scope of their research as 300 people across 3 sites.

----
